CUNY SPS DATA 605 Final

### 2019-05-23 DATA605/MSilva_Final.Rmd
More work on the final

```{r}
exponential_pdf <- fitdistr(kaggle$BsmtUnfSF, densfun = "exponential")
```

*The optimal value for $\lambda$ is `r exponential_pdf$estimate`.*

```{r}
samples <- rexp(10000, rate = exponential_pdf$estimate)
```

@@

*The original data is not quite exponential, but it's not a bad approximation.  It has a longer tail than the data.*

@@

```{r}

```

@@

```{r}
library(randomForest)
library(caret)

@@

ctrl <- trainControl(method = "cv", number = 5)
rf_fit <- train(SalePrice ~ ., data = rf_data, method = "rf", trControl = ctrl, importance = TRUE, verbose = TRUE)
```

>>>>

```{r}
lambda <- fitdistr(kaggle$BsmtUnfSF, densfun = "exponential")$estimate
```

*The optimal value for $\lambda$ is `r lambda`.*
```{r}
samples <- rexp(10000, rate = lambda)
```

@@

*The original data is not quite exponential, but it's not a bad approximation.  The exponential distribution data has a longer tail than the basement square footage data.*

@@

*The PDF would be $f(x;\lambda) = \lambda e^{-\lambda x}$ where $x \geq 0$ and otherwise zero.*

*The CDF would be $F(x;\lambda) = 1 - e^{-\lambda x}$.  lambda is `r lambda`. To find the 5th percentile we need to solve for x in:*

$$0.05 = 1 - e^{-`r lambda` x}$$

$$-0.95 = - e^{-`r lambda` x}$$

$$-ln(0.95) = `r lambda` x$$

$$x = \frac{-ln(0.95)}{`r lambda`} = `r -log(0.95)/lambda`$$
*For the 95th percentile we need to solve for x in:*

$$0.95 = 1 - e^{-`r lambda` x}$$

$$-0.05 = - e^{-`r lambda` x}$$

$$-ln(0.05) = `r lambda` x$$

$$x = \frac{-ln(0.05)}{`r lambda`} = `r -log(0.05)/lambda`$$

*So the 5th and 95th percentiles are approximately `r round(-log(0.95)/lambda,0)` and `r round(-log(0.05)/lambda,0)`, respectively.*

@@

```{r, cache=TRUE, message=FALSE, warning=FALSE}
library(randomForest)
library(caret)

set.seed(12345)

@@

ctrl <- trainControl(method = "cv", number = 10)
rf_fit <- train(SalePrice ~ ., data = rf_data, method = "rf", trControl = ctrl, importance = TRUE, verbose = TRUE)
```

*Now we can examine the variable importance*

```{r}
imp_var <- importance(rf_fit$finalModel) 
variables <- rownames(imp_var)

imp_var <- imp_var %>%
  as.data.frame()

names(imp_var) <- c("IncMSE", "IncNodePurity")
imp_var$Variable <- variables

imp_var %>%
  select(Variable, IncMSE, IncNodePurity) %>%
  arrange(-IncMSE) %>%
  kable() %>%
  kable_styling()
```
